---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r echo = TRUE}
data <- read.csv("activity.csv", header = T)
data$date <- as.Date(data$date, format = "%Y-%m-%d")
```

## What is mean total number of steps taken per day?

**Q1: Calculate the total number of steps taken per day**
```{r echo = TRUE}
numOfStepsPerDay <- aggregate(data$steps, by = list(data$date), FUN = "sum")
colnames(numOfStepsPerDay) <- c("Date", "Total_Steps")
```

**Q2: Make a histogram of the total number of steps taken each day**
```{r echo = TRUE}
library(ggplot2)
ggplot(numOfStepsPerDay, aes(Total_Steps)) + 
	geom_histogram(binwidth = 1000, fill = "steelblue", color = "black") +
	labs(title = "Histogram of Total steps per Day", x = "Total steps per Day")
```

**Q3: Calculate and report the mean and median of the total number of steps taken per day**
* Mean of the total number of steps taken per day
```{r echo = TRUE}
mean(numOfStepsPerDay$Total_Steps, na.rm = T)
```

* Median of the total number of steps taken per day
```{r echo = TRUE}
median(numOfStepsPerDay$Total_Steps, na.rm = T)
```
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
